\documentclass[hidelinks,10pt]{my_cv}

\usepackage[margin=0.6in, bottom=0.5in, top=0.4in]{geometry}
\usepackage{fancyhdr}
\usepackage{xcolor}
\usepackage{changepage}

\renewcommand{\familydefault}{\sfdefault}		% Changes default text to sans-serif

%\fontfamily{phv}\selectfont

\begin{document}

\null\hfill\begin{tabular}[t]{l@{}}
  \textit{Current as of: 1 June 2020}
\end{tabular}

\name{Will Simmons}

\centerline{Columbia University, New York, NY}
\contact{\href{mailto:simm.will@gmail.com}{simm.will@gmail.com}}{808-202-3157}{\href{https://simmwill.github.io}{simmwill.github.io}}{}{}

% EDUCATION --------------------------------------------------------------------------------------
\section{Education}

	\datedsubsection{Master of Public Health, Epidemiology \& Applied Biostatistics}{Aug. 2018 - May 2020}
	Columbia University, Mailman School of Public Health, New York, NY% 	\hfill  \textit{\raiseup{(anticipated)}}

	\vspace{2mm}

	%\\{Focuses: environmental epidemiology, biostatistical and data science methods		\hfill		 GPA: 4.0}
	{\textit{Relevant coursework:} epidemiological study design, biostatistical methods (regression/GLMs, survival analysis, \hfill   GPA: 4.0} 
	\\{longitudinal analysis), environmental health modeling, pharmaceutical statistics, machine learning, data and}
	\\{database management, statistical programming (R, SAS, SQL)}

	\datedsubsection{Bachelor of Science, Neuroscience}{Aug. 2011 - May 2015}
	Baylor University, Waco, TX

	\vspace{2mm}
	
	{\textit{Relevant coursework:} neuroanatomy \& physiology, community-based health research, biostatistics, mixed models,	\hfill GPA: 4.0}
	\\{pre-medical studies}

% Scholarships and Honors was here - moved below

% RESEARCH --------------------------------------------------------------------------------------
\section{Current and Previous Research}

	\datedsubsection{Fine particulate matter, extreme heat events, and congenital heart defects}{Nov. 2019 - present}
	\vspace{0.2mm}
%	{Graduate Research supervised by {\href{https://www.mailman.columbia.edu/people/our-faculty/js5406}{Dr. Jeanette Stingone}}
	{Department of Epidemiology, Columbia University Mailman School of Public Health}
	\subitemssss
		%{Supervisor: {\href{https://www.mailman.columbia.edu/people/our-faculty/js5406}{Dr. Jeanette Stingone}}}
		{Conducting large, population-based case-control study on environmental risk factors for birth defects in US}
		{Investigate relationships between maternal exposures (extreme heat events, PM\textsubscript{2.5}) and congenital heart defect subtypes}
		{Prepare and analyze data from the National Birth Defects Prevention Study (NBDPS), largest US study of its kind}
		{Supported by nationwide research sites and the Centers for Disease Control (CDC) \textcolor{blue}{\href{https://www.cdc.gov/ncbddd/birthdefects/nbdps.html}{(info)}}}

	\datedsubsection{Climate variation and under-5 weight-for-height}{Feb. 2019 - present}
	\vspace{0.2mm}
%	{Graduate Research supervised by {\href{http://www.lse.ac.uk/GranthamInstitute/profile/hannah-nissan/}{Dr. Hannah Nissan}} and {\href{https://robbiemparks.github.io/}{Dr. Robbie Parks}}
	{International Research Institute for Climate \& Society, Earth Institute, Columbia University}
	\subitemssss
		%{Supervisors: {\href{http://www.lse.ac.uk/GranthamInstitute/profile/hannah-nissan/}{Dr. Hannah Nissan}} and {\href{https://robbiemparks.github.io/}{Dr. Robbie Parks}}}
		{Conducted large, population-based time series study on climatic risk factors for child development in Bangladesh}
		{Investigated associations between extreme climate events and child anthropometry at seasonal and sub-seasonal scales}
		{Merged, harmonized, and analyzed large, administrative climate and nutrition surveillance databases}
		{Contributed biostatistical/epidemiological skillset to multidisciplinary team of top Columbia researchers for ACToday \textcolor{blue}{\href{https://iri.columbia.edu/actoday/}{(info)}}}

	\datedsubsection{Water quality, food security, and under-5 anthropometry}{Jan. 2013 - May 2015}
	\vspace{0.2mm}
%	{Undergraduate Resarch Assistant to Prof. Lisa Baker, MD PhD}
	{Baylor University, Waco, TX}
	\subitemsss
		%{Supervisor: Prof. Lisa Baker, MD PhD}
		{Led data collection and analysis for study of dietary and environmental risk factors for child development}
		{Investigated associations between dietary diversity, water quality, and anthropometry in indigenous Luo community}
		{Analyses leveraged for local capacity building in community-led water and nutrition interventions, utilized by 1,000+}


% SCHOLARSHIPS AND HONORS --------------------------------------------------------------------------------------
\section{Scholarships, Honors, and Professional Memberships}
	
	{Member, American Statistical Association   \hfill 2020 - present}
	\\{1st prize - research poster presentation, NYC Clinical Climate Change Conference, Mt. Sinai \hfill 2020}
	\\{1st place - research presentation, Master's Student Day, Columbia Dept. of Epidemiology \hfill 2019
	\\{Delta Omega Honor Society \hfill 2019}
	\\{Wyman Scholar, Columbia University (full tuition) \hfill 2018}  % : \$80,000
	\\{Outstanding Student in Neuroscience, Baylor University \hfill 2015}
	\\{Phi Beta Kappa Honor Society \hfill 2014}
	\\{Glennis McCrary Goodrich Scholarship Award for International Research (\$3,500) \hfill 2013}
	\\{Regent's Gold Scholar, Baylor University (full tuition) \hfill 2011}  % : \$138,000



% OTHER EXPERIENCE --------------------------------------------------------------------------------------
\section{Teaching and Professional Experience}

	\datedsubsection{Graduate Teaching Assistant}{Aug. 2019 - Dec. 2019}
	{Departments of Biostatistics \& Epidemiology, Columbia University Mailman School of Public Health}
	\subitemss
		{Teaching assistant for graduate-level Quantitative Methods module in Columbia MSPH's CORE Curriculum}
		{Instructed 25 first-year master's students once weekly in introductory biostatistics and epidemiology}

	\datedsubsection{Food Systems Specialist}{Aug. 2015 - Jul. 2018}
	{Hawai`i Alliance for Community-Based Economic Development, Honolulu, HI}
	\subitemss
		%{Coordinated interisland network of 20+ grassroots organizations in indigenous health and environmental justice}
		{Coordinator and intermediary for network of practitioners and policymakers in indigenous health and environmental justice}
		%{Wrote successful grant proposals and contracts totaling \$600,000+ for community food systems work}
		{Wrote successful grant proposals and contracts totaling \$600,000+ for grassroots organizational capacity building}
		%{Led 3-year contract with Roman Catholic Diocese to integrate (1) sustainability education and (2) organizational planning across interisland network of 15 organizations, parishes, and schools}
		%{Non-Competitive Eligibility (NCE): term ended 10/30/2017, after which enrolled in graduate program 08/31/2018}
		%{Two-term AmeriCorps VISTA and subsequent full-time staff member}

	\datedsubsection{Lead Program Evaluator}{May 2015 - Aug. 2015}
	{Our Children, Their Nutrition}
	\subitemss
		{Led data analytics, monitoring, and evaluation of childhood nutrition education program}
		{Contributed to research presented at American Public Health Association (APHA) 2015 Annual Meeting}

%	\datedsubsection{Development Intern, Africa Bureau}{Jun. 2014 - Aug. 2014}
%	{United States Agency for International Development (USAID), Washington, DC}
%	\subitemss
%		{Provided technical and capacity building support to Country Development Officers throughout Southern Africa}
%		{Created briefing materials for high-level initiatives, including President Barack Obama's Young African Leaders Initiative}


% PUBLICATIONS --------------------------------------------------------------------------------------
\section{Publications}

%\vspace{0.5mm}
	\textit{In preparation:}

		\vspace{1mm}
		
		\begin{adjustwidth}{2.5em}{0pt}

		{\textbf{Simmons W}, Stingone J, Luben T, Sheridan S, Langlois P, Shaw G, Reefhuis J, Romitti P, Feldkamp M, Nembhard W, Browne M, Lin S, and the National Birth Defects Prevention Study. Joint effects of prenatal exposure to fine particulate matter and extreme heat on congenital heart defects in offspring. \textit{   [Anticipated submission: Summer 2020.]}}
%		\\ \\
%		{\textbf{Simmons W}, Parks RM, Downs S, Nissan H. Time series analysis of associations between extreme climate events and under-5 growth faltering: Bangladesh, 1990-2006. \textit{   [On hold due to COVID-19.]}}

		\end{adjustwidth}

% PRESENTATIONS --------------------------------------------------------------------------------------
\section{Presentations and Conferences}

	\textbf{Simmons W}, Nissan H (2020). \textit{Climate variation and anthropometric indicators of under-5 nutrition: Bangladesh, 1990-2006.} Poster, 2nd Annual Conference on Clinical Climate Change. Icahn School of Medicine at Mount Sinai. New York, NY. First prize.
	\\ \\
	Research Computing Bootcamp: UNIX, Git, Python (2020). Attendee. Columbia University. New York, NY.
	\\ \\
	"Food, climate, and environment: What's next?" (2019). Panel moderator and organizer. Columbia University Mailman School of Public Health. New York, NY.
	\\ \\
	\textbf{Simmons W}, Nissan H (2019). \textit{Associations between climate and under-5 nutritional status in Bangladesh, 1990-2006.} Invited presentation, Epi Master’s Student Day. Columbia University Mailman School of Public Health. New York, NY. First prize.
	\\ \\
	\textbf{Simmons W}, Baker L (2016). \textit{Clean water, food security, or protein?  A study of growth among children in rural western Kenya.} Contributor to presentation, 13th Annual Global Health \& Innovation Conference. Yale University, New Haven, CT.

%	\datedsubsection{}

% SKILLS --------------------------------------------------------------------------------------
\section{Skills}

	\subsection{Languages, Software, \& Tools					\hfill				Certifications}
		\vspace{1mm}
		{Proficient: R (ggplot2, tidyverse, caret), SAS, SQL (MySQL, MS Access), Zotero		\hfill				HIPAA, CITI Human Subjects}
		\\{Familiar: \textcolor{white}{rr}Git/DVCS, \LaTeX, R Shiny, MATLAB, QGIS}  % White text to add some space
	
%	\subsection{Tools}
%		\vspace{1mm}
%		{Familiar: Git/DVCS, \LaTeX}  

\newpage

% REFERENCES --------------------------------------------------------------------------------------
%\section{References}
%
%
%	\textbf{Christine Mauro, PhD} - Supervisor, Graduate Teaching Assistantship
%	\\Assistant Professor, Biostatistics
%	\\Columbia University Mailman School of Public Health
%	\\212-305-2329	
%	\\ \href{mailto:cmm2212@cumc.columbia.edu}{cmm2212@cumc.columbia.edu}
%
%	\vspace{5mm}
%
%	\textbf{Jeanette Stingone, PhD} - Research Advisor, Master's Thesis
%	\\ Assistant Professor, Epidemiology 
%	\\ Columbia University Mailman School of Public Health  
%	\\ 212-305-9407
%	\\ \href{mailto:js5406@cumc.columbia.edu}{js5406@cumc.columbia.edu}
%	
%	\vspace{5mm}
%
%	\textbf{Hannah Nissan, PhD} - Research Advisor, Earth Institute, Columbia University
%	\\Associate Research Scientist
%	\\International Research Institute for Climate and Society, Columbia University
%	\\Centre for Analysis of Time Series, London School of Economics and Political Science
%	\\ \href{mailto:hannah@iri.columbia.edu}{hannah@iri.columbia.edu}





\end{document}












% Old references code


%	{\textbf{Jeanette Stingone, PhD}   \hspace{4.7mm} Research Advisor, Master's Thesis   \hfill   js5406@cumc.columbia.edu}
%	\\{\textbf{Christine Mauro, PhD}   \hspace {8mm} Supervisor, Graduate Teaching Assistantship   \hfill   cmm2212@cumc.columbia.edu}
%	\\{\textbf{Hannah Nissan, PhD}   \hspace{9.75mm} Research Advisor, Earth Institute at Columbia University \hfill   hannah@iri.columbia.edu}







% Other old code


%  "Current & Previous Research"
%  "Teaching & Professional Experience"
%  "Presentations"
%  "Skills"


%	\newline{- Research Advisor: Prof. Lisa Baker MD PhD}
%	\newline{- Readers: Prof. Keith Stanford PhD, Prof. Jim Patton PhD}
%	\newline{- Thesis: ``Cross-sectional study of relative associations of nutrition and water quality with child body size in a rural Kenyan community."}
